%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.7in,top=0.4in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\usepackage{romannum}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{enumitem}


%----------------------------------------------------------------------------------------
%   DOCUMENT START
%----------------------------------------------------------------------------------------
\name{Ezra Skoog} % Your name
\address{(910)~$\cdot$~850~$\cdot$~7049 \\ ezraskoog@yahoo.com \\ https://github.com/Ezra1285 \\ www.linkedin.com/in/ezra-skoog
} % Your phone number and email
\begin{document}
\title{Ezra's Resume}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Montana State University}{Graduation Date: May 2024}{BS.in Computer Science }{Overall GPA: 3.7}
{Related Courses:} {Calculus \Romannum{1} \& \Romannum{2}, Data structures and algorithms \Romannum{1} \& \Romannum{2}, Embedded Systems, Web Design, Robotic Vision, Computer Security, Networks, Database Systems, Programming with c, Software Engineering, System Administration, Discrete Structures, Compilers, and Linear Algebra.}

\end{rSubsection}


%\vspace{-.1cm}
\vspace{-.65cm}
\item[]

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Ascent Vision Technologies}{June 2022 - Present}{Software Engineering Intern}{Belgrade, MT}
\begin{itemize}[leftmargin=*, label={}]
\setlength\itemsep{-1.7em}
\item -Worked with our Production team to fully automate the setup process of our passive radar systems using a Raspberry Pi. \\
\item -Created an automated test cycler in order to find a rare bug case in our gyro-stabilized camera EO lenses and video stream. \\
\item -Developed an algorithm to detect and correct dead pixels through an IR lens.\\
\item -Helped with implementing new front-end features for the gimbals GUI.  \\
\item -Assisted with developing and testing unit/regression tests for new software releases. 
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Foundant Technologies}{November 2021 - May2022}{Client Service Intern}
{Bozeman, MT}
\begin{itemize}[leftmargin=*, label={}]
\setlength\itemsep{-1.7em}
\item -Identified customer needs through active listening techniques to help build a relationship with the customer. \\
\item -Continuously gained product knowledge through discussing difficult problems and keeping up to date with new releases. \\
\item -Demonstrated the ability to think and act quickly in dynamic situations.
\end{itemize}
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%   Technical Experience 
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
\begin{rSubsection}{Inventory Management System } {April 2022}{}{}
\item[]\href{https://github.com/turnerburchard/322-inventory}{\emph{github.com/InventoryManagement}}
\item Worked with a team using the SCRUM development process to complete a sprint.
\item Created and utilized UML 2.0 models, including uses cases, class diagrams, activity diagrams, and sequence diagrams.
\item Implemented various design patterns such as the singleton and observer pattern.
\end{rSubsection}
\begin{rSubsection}{Educational Cryptocurrency Website} {November 2021}{}{}
\item[]\href{https://github.com/Ezra1285/CryptoEducation}{\emph{github.com/Crypto}}
\item Gained knowledge of a complex technology and then presented that information in a way that anyone can understand.
\item Utilized flexbox and grid models to acquire a better understanding of website design.
\end{rSubsection}
\iffalse
\begin{rSubsection}{UUP SIAM - Direct Tap Machine Learning}{April 2017 - Present}{}{City One, UP}
\item Built a model to visualize the correlation between order quantity and seasonality, using Python pandas and matplotlib
\end{rSubsection}
\fi
\iffalse
\begin{rSubsection}{JavaScript 8 Puzzle Solver}{December 2016}{}{}
\item Developed a sliding puzzle solver in pure JavaScript to animate a step by step solution
\item Is able to solve 3x3 tile board in less than 1 second using the A* algorithm
\end{rSubsection}
\fi
\end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
% \iffalse
\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C/C++, Java, HTML/CSS, LaTex \\
Tools & Microprocessors, Ubuntu, Git, Wire-shark, FLTK C++, VMware \\
\end{tabular}

\end{rSection}
% \fi
%----------------------------------------------------------------------------------------
%   INTERESTS
%----------------------------------------------------------------------------------------
\iffalse
\begin{rSection}{Interests}
Cycling\hspace{1cm}Basketball\hspace{1cm}Soccer\hspace{1cm}Automation\hspace{1cm}Electronics Hobbyist
\end{rSection}
\fi
%----------------------------------------------------------------------------------------

\end{document}
